---
title: "NE 2019 Hunter Analysis and Sample Pull"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(dbplyr)
library(DT)
library(tidyr)
library(readr)
library(readxl)
library(tibble)
library(lubridate)
library(stringr)
library(Hmisc)
library(anesrake)
library(weights)
library(haven)

knitr::opts_chunk$set(comment = NA)
```

## R Markdown
```{r}
lic_sales<- read_excel("E:/SA/Data-sensitive/WMI-19-01/State License Records for National Survey/NEGP/Southwick_03.06.2020_List of 2019 Hunting Permit Owners.xlsx")
```

Removing Fur Harvest Permit and Non Resident Records
```{r}
lic_sales<-lic_sales[!lic_sales$PermitGroup=="Fur Harvest Permits",]
lic_sales<-lic_sales[!lic_sales$CustomerResident=="F",]
```

Creating a customer database
```{r}
cust<-lic_sales
cust<- distinct(cust, OwnerCustomerUID, .keep_all = TRUE) %>%
  select(OwnerCustomerUID,dob,email,firstName,lastName,Sex)
```

Adding binary variables to indicate Annual, Lifetime, Big Game and Combo license purchases 
```{r}
lic_sales$Combo<- 
  ifelse(lic_sales$PermitGroup == "Hunt Fish Combo Permits", 1, 0)

lic_sales$BG<- 
  ifelse(lic_sales$PermitGroup == "Big Game Permits", 1, 0)

lic_sales$Lifetime<- 
  ifelse(grepl("Lifetime",lic_sales$PermitName)==TRUE,1,0)

lic_sales$Annual<- 
  ifelse(lic_sales$Combo==0 & lic_sales$BG==0 & lic_sales$Lifetime==0,1,0)
```

Adding license purchase observations to customer database (cust)
```{r}
#Combo Licenses______________________________________________
cust %>% group_by(OwnerCustomerUID) 
filter(lic_sales, Combo>=1) 
y_customers <- as.data.frame(filter(lic_sales, Combo==1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, Combo)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#Annual Hunt Licenses________________________________________
filter(lic_sales, Annual>=1) 
y_customers <- as.data.frame(filter(lic_sales, Annual>=1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, Annual)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#Lifetime Licenses______________________________________________
cust %>% group_by(OwnerCustomerUID) 
filter(lic_sales, Lifetime>=1) 
y_customers <- as.data.frame(filter(lic_sales, Lifetime==1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, Lifetime)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#BG Licenses______________________________________________
cust %>% group_by(OwnerCustomerUID) 
filter(lic_sales, BG>=1) 
y_customers <- as.data.frame(filter(lic_sales, BG==1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, BG)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#Turn NAs for missing licenses into 0s for counting purposes
cust[is.na(cust)] <- 0
```

Calculate age group based on birthdate
```{r}
cust$dob<-as.Date.factor(cust$dob)

cust$age <- 2019 - year(cust$dob)

cust$age_group <- 
  ifelse((0 <= cust$age & cust$age < 18), "17 or younger",
  ifelse((18 <= cust$age & cust$age <= 24), "18 to 24", 
  ifelse((25 <= cust$age & cust$age <= 34), "25 to 34", 
  ifelse((35 <= cust$age & cust$age <= 44), "35 to 44", 
  ifelse((45 <= cust$age & cust$age <= 54), "45 to 54", 
  ifelse((55 <= cust$age & cust$age <= 64), "55 to 64", 
  ifelse((65 <= cust$age), "65+", 
  "broken"
)))))))

#Dropping customers under 18
cust<-cust[!(cust$age_group=="17 or younger"),]
```

Drop one case missing gender info
```{r}
cust<-cust[!(cust$Sex=="NULL"),]
```

Printing Demographics for License Population
```{r}
#Age Groups
age_table<-cbind(table(cust$age_group),prop.table(table(cust$age_group)))
colnames(age_table)<-c("count","percent")

view(age_table)
write.csv(age_table, file = "NE_hunter_age.csv")

#Sex
gender_table<-cbind(table(cust$Sex),prop.table(table(cust$Sex)))
colnames(gender_table)<-c("count","percent")

view(gender_table)
write.csv(gender_table, file = "NE_hunter_gender.csv")

#Annual License
annual_table<-cbind(table(cust$Annual),prop.table(table(cust$Annual)))
colnames(annual_table)<-c("count","percent")

view(annual_table)
write.csv(annual_table, file = "NE_Annual_Hunt_Lic.csv")

#Combo License
combo_table<-cbind(table(cust$Combo),prop.table(table(cust$Combo)))
colnames(combo_table)<-c("count","percent")

view(combo_table)
write.csv(combo_table, file = "NE_Combo_Hunt_Lic.csv")

#Lifetime License
lifetime_table<-cbind(table(cust$Lifetime),prop.table(table(cust$Lifetime)))
colnames(lifetime_table)<-c("count","percent")

view(lifetime_table)
write.csv(lifetime_table, file = "NE_Lifetime_Hunt_Lic.csv")

#BG License
BG_table<-cbind(table(cust$BG),prop.table(table(cust$BG)))
colnames(BG_table)<-c("count","percent")

view(BG_table)
write.csv(BG_table, file = "NE_BG_Hunt_Lic.csv")
```

Creating subset of hunters with email addresses
```{r}
svy<-subset(cust,cust$email!="")
svy<-subset(svy,grepl("@",svy$email)=="TRUE")

#Convert variable types to Factor
svy$age_group<-as.factor(svy$age_group)
svy$Sex<-as.factor(svy$Sex)
svy$Combo<-as.factor(svy$Combo)
svy$Annual<-as.factor(svy$Annual)
svy$BG<-as.factor(svy$BG)
svy$Lifetime<-as.factor(svy$Lifetime)

svy <- as.data.frame(svy)
```

Defining Population Statistics
```{r}
pop <- list(
    age_group = c("18 to 24" = 0.1102475,
                  "25 to 34" = 0.1732647,
                  "35 to 44" = 0.1684022,
                  "45 to 54" = 0.1387159,
                  "55 to 64" = 0.1473531,
                  "65+" = 0.2620168),
    Sex = c("Male" = 0.8866844, "Female" = 0.1133156),
    Annual = c("0" = 0.8408766, "1" = 0.1591234),
    Combo = c("0" = 0.567796,"1" = 0.432204),
    Lifetime= c("0" = 0.991911341, "1" = 0.008088659),
    BG= c("0"= 0.3412949, "1"= 0.6587051))
```

Weighting function to be used on email list
```{r}
est_wts <- function(
    svy, pop, print_name = "", idvar = "OwnerCustomerUID", cap = 20
) {
    # run weighting
    wts <- anesrake(pop, svy, caseid = svy[[idvar]], force1 = TRUE, cap = cap)
    
    # print summary
    cat("\nWeight Summary for", print_name, "-----------------------------\n\n")
    print(summary(wts))
    
    # return output
    svy$rake_wt <- wts$weightvec
    svy
}
```

Run Weighting
```{r}
cust_wt<- est_wts(svy, pop)
```

Pull weighted sample of 1000 emails
```{r}
ne_email_list<-sample_n(cust_wt, 1000,  weight = cust_wt$rake_wt)
write.csv(ne_email_list, file = "NE_sample_contacts.csv")
```

Printing Demographics for sample
```{r}
#Age Groups
age_table<-cbind(table(ne_email_list$age_group),prop.table(table(ne_email_list$age_group)))
colnames(age_table)<-c("count","percent")

write.csv(age_table, file = "ne_Email_Pop_age.csv")

#Gender
gender_table<-cbind(table(ne_email_list$Sex),prop.table(table(ne_email_list$Sex)))
colnames(gender_table)<-c("count","percent")

write.csv(gender_table, file = "ne_Email_Pop_gender.csv")

#Annual License
annual_table<-cbind(table(ne_email_list$Annual),prop.table(table(ne_email_list$Annual)))
colnames(annual_table)<-c("count","percent")

write.csv(annual_table, file = "ne_Email_Pop_Annual_Hunt_Lic.csv")

#Combo License
combo_table<-cbind(table(ne_email_list$Combo),prop.table(table(ne_email_list$Combo)))
colnames(combo_table)<-c("count","percent")

write.csv(combo_table, file = "ne_Email_Pop_Combo_Hunt_Lic.csv")

#Lifetime License
Lifetime_table<-cbind(table(ne_email_list$Lifetime),prop.table(table(ne_email_list$Lifetime)))
colnames(Lifetime_table)<-c("count","percent")

write.csv(Lifetime_table, file = "ne_Email_Pop_Lifetime_Hunt_Lic.csv")

#BG License
BG_table<-cbind(table(ne_email_list$BG),prop.table(table(ne_email_list$BG)))
colnames(BG_table)<-c("count","percent")

write.csv(BG_table, file = "ne_Email_Pop_BG_Hunt_Lic.csv")
```
