---
title: "SD Hunters 2019 Sample Pull"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(dbplyr)
library(DT)
library(tidyr)
library(readr)
library(readxl)
library(tibble)
library(lubridate)
library(stringr)
library(Hmisc)
library(anesrake)
library(weights)
library(haven)

knitr::opts_chunk$set(comment = NA)
```

## R Markdown
```{r}
lic_sales<- read_excel("E:/SA/Data-sensitive/WMI-19-01/State License Records for National Survey/NEGP/Southwick_03.06.2020_List of 2019 Hunting Permit Owners.xlsx")
```

Removing Fur Harvest Permit and Non Resident Records
```{r}
lic_sales<-lic_sales[!lic_sales$PermitGroup=="Fur Harvest Permits",]
lic_sales<-lic_sales[!lic_sales$CustomerResident=="F",]
```

Creating a customer database
```{r}
cust<-lic_sales
cust<- distinct(cust, OwnerCustomerUID, .keep_all = TRUE) %>%
  select(OwnerCustomerUID,dob,email,firstName,lastName,Sex)
```

Adding binary variables to indicate Annual, Lifetime, Big Game and Combo license purchases 
```{r}
lic_sales$Combo<- 
  ifelse(lic_sales$PermitGroup == "Hunt Fish Combo Permits", 1, 0)

lic_sales$BG<- 
  ifelse(lic_sales$PermitGroup == "Big Game Permits", 1, 0)

lic_sales$Lifetime<- 
  ifelse(grepl("Lifetime",lic_sales$PermitName)==TRUE,1,0)

lic_sales$Annual<- 
  ifelse(lic_sales$Combo==0 & lic_sales$BG==0 & lic_sales$Lifetime==0,1,0)
```

Adding license purchase observations to customer database (cust)
```{r}
#Combo Licenses______________________________________________
cust %>% group_by(OwnerCustomerUID) 
filter(lic_sales, Combo>=1) 
y_customers <- as.data.frame(filter(lic_sales, Combo==1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, Combo)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#Annual Hunt Licenses________________________________________
filter(lic_sales, Annual>=1) 
y_customers <- as.data.frame(filter(lic_sales, Annual>=1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, Annual)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#Lifetime Licenses______________________________________________
cust %>% group_by(OwnerCustomerUID) 
filter(lic_sales, Lifetime>=1) 
y_customers <- as.data.frame(filter(lic_sales, Lifetime==1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, Lifetime)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#BG Licenses______________________________________________
cust %>% group_by(OwnerCustomerUID) 
filter(lic_sales, BG>=1) 
y_customers <- as.data.frame(filter(lic_sales, BG==1)) %>% 
  unique() %>% 
  select(OwnerCustomerUID, BG)
cust <- left_join(cust, y_customers, by = "OwnerCustomerUID") %>% unique()
rm(y_customers)

#Turn NAs for missing licenses into 0s for counting purposes
cust[is.na(cust)] <- 0
```
Calculate age group based on birthdate
```{r}
cust$DateOfBirth<-as.Date.factor(cust$DateOfBirth)

cust$age <- 2019 - year(cust$DateOfBirth)

cust$age_group <- 
  ifelse((0 <= cust$age & cust$age < 18), "17 or younger",
  ifelse((18 <= cust$age & cust$age <= 24), "18 to 24", 
  ifelse((25 <= cust$age & cust$age <= 34), "25 to 34", 
  ifelse((35 <= cust$age & cust$age <= 44), "35 to 44", 
  ifelse((45 <= cust$age & cust$age <= 54), "45 to 54", 
  ifelse((55 <= cust$age & cust$age <= 64), "55 to 64", 
  ifelse((65 <= cust$age), "65+", 
  "broken"
)))))))

#Dropping customers under 18
cust<-cust[!(cust$age_group=="17 or younger"),]
```

Cleaning up the Gender varaible
```{r}
cust$Gender <- 
  ifelse(cust$Gender=="Male", "M",
  ifelse(cust$Gender=="M", "M", 
  ifelse(cust$Gender=="F","F", "missing")))
```

Printing Demographics for License Population
```{r}
#Age Groups
age_table<-cbind(table(cust$age_group),prop.table(table(cust$age_group)))
colnames(age_table)<-c("count","percent")

view(age_table)
write.csv(age_table, file = "SD_hunter_age.csv")

#Gender
gender_table<-cbind(table(cust$Gender),prop.table(table(cust$Gender)))
colnames(gender_table)<-c("count","percent")

write.csv(gender_table, file = "SD_hunter_gender.csv")

#Annual License
annual_table<-cbind(table(cust$Annual),prop.table(table(cust$Annual)))
colnames(annual_table)<-c("count","percent")

write.csv(annual_table, file = "SD_Annual_Hunt_Lic.csv")

#Combo License
combo_table<-cbind(table(cust$Combo),prop.table(table(cust$Combo)))
colnames(combo_table)<-c("count","percent")

write.csv(combo_table, file = "SD_Combo_Hunt_Lic.csv")
```

Creating subset of hunters with email addresses
```{r}
svy<-subset(cust,cust$EmailAddress!="")
svy<-subset(svy,grepl("@",svy$EmailAddress)=="TRUE")

#Convert variable types to Factor
svy$age_group<-as.factor(svy$age_group)
svy$Gender<-as.factor(svy$Gender)
svy$Combo<-as.factor(svy$Combo)
svy$Annual<-as.factor(svy$Annual)
```

Defining Population Statistics
```{r}
pop <- list(
    age_group = c("18 to 24" = 0.1373835,
                  "25 to 34" = 0.1828647,
                  "35 to 44" = 0.1856015,
                  "45 to 54" = 0.1535746,
                  "55 to 64" = 0.1768688,
                  "65+" = 0.1637070),
    Gender = c("M" = 0.877083943, "F" = 0.120680650, 
               "missing" = 0.002235407),
    Annual = c("0" = 0.2108281,"1" = 0.7891719),
    Combo = c("0" = 0.4020077,"1" = 0.5979923))
```

Weighting function to be used on email list
```{r}
est_wts <- function(
    svy, pop, print_name = "", idvar = "HunterID", cap = 20
) {
    # run weighting
    wts <- anesrake(pop, svy, caseid = svy[[idvar]], force1 = TRUE, cap = cap)
    
    # print summary
    cat("\nWeight Summary for", print_name, "-----------------------------\n\n")
    print(summary(wts))
    
    # return output
    svy$rake_wt <- wts$weightvec
    svy
}
```

Run Weighting
```{r}
cust_wt <- est_wts(svy, pop)
```

Weighting is unnessessary, because subset of hunters with valid email addresses already resemble the larger hunting population so closely. See demographics of records with valid email below:

Printing Demographics for sample
```{r}
#Age Groups
age_table<-cbind(table(svy$age_group),prop.table(table(svy$age_group)))
colnames(age_table)<-c("count","percent")

write.csv(age_table, file = "SD_Email_List_age.csv")

#Gender
gender_table<-cbind(table(svy$Gender),prop.table(table(svy$Gender)))
colnames(gender_table)<-c("count","percent")

write.csv(gender_table, file = "SD_Email_List_gender.csv")

#Annual License
annual_table<-cbind(table(svy$Annual),prop.table(table(svy$Annual)))
colnames(annual_table)<-c("count","percent")

write.csv(annual_table, file = "SD_Email_List_Annual_Hunt_Lic.csv")

#Combo License
combo_table<-cbind(table(svy$Combo),prop.table(table(svy$Combo)))
colnames(combo_table)<-c("count","percent")

write.csv(combo_table, file = "SD_Email_List_Combo_Hunt_Lic.csv")
```


Instead of weighting, we'll take a simple random sample of those hunters with valid email addresses. We'll examine the demographics of this sample and confirm that they closely resemble the greater hunter population in SD.

Pull weighted sample of 1000 emails
```{r}
sd_email_list<-sample_n(svy, 1000)
write.csv(sd_email_list, file = "SD_sample_contacts.csv")
```

Printing Demographics for sample
```{r}
#Age Groups
age_table<-cbind(table(sd_email_list$age_group),prop.table(table(sd_email_list$age_group)))
colnames(age_table)<-c("count","percent")

write.csv(age_table, file = "SD_Email_Pop_age.csv")

#Gender
gender_table<-cbind(table(sd_email_list$Gender),prop.table(table(sd_email_list$Gender)))
colnames(gender_table)<-c("count","percent")

write.csv(gender_table, file = "SD_Email_Pop_gender.csv")

#Annual License
annual_table<-cbind(table(sd_email_list$Annual),prop.table(table(sd_email_list$Annual)))
colnames(annual_table)<-c("count","percent")

write.csv(annual_table, file = "SD_Email_Pop_Annual_Hunt_Lic.csv")

#Combo License
combo_table<-cbind(table(sd_email_list$Combo),prop.table(table(sd_email_list$Combo)))
colnames(combo_table)<-c("count","percent")

write.csv(combo_table, file = "SD_Email_Pop_Combo_Hunt_Lic.csv")
```
