---
title: "Untitled"
author: "Ben"
date: "March 9, 2020"
output: ht```{r setup, include=FALSE}
library(dplyr)
library(dbplyr)
library(DT)
library(tidyr)
library(readr)
library(readxl)
library(tibble)
library(lubridate)
library(stringr)
library(Hmisc)
library(anesrake)
library(weights)
library(haven)

knitr::opts_chunk$set(comment = NA)
```ml_document
---


Read in VA Records
```{r}
cust<- read.delim("C:/Users/sbscu/Desktop/WMI-19-01/National Survey Effort/State License Data Tranfer Files/VA-DGIF/Customers.txt", header = TRUE, sep="\t", fill=TRUE, encoding="UTF-8")

lic<- read.delim("C:/Users/sbscu/Desktop/WMI-19-01/National Survey Effort/State License Data Tranfer Files/VA-DGIF/License.txt", header = TRUE, sep="\t", fill=TRUE, encoding="UTF-8")

lic_sales_annual<-read.delim("C:/Users/sbscu/Desktop/WMI-19-01/National Survey Effort/State License Data Tranfer Files/VA-DGIF/License_Sales_Annual.txt", header = TRUE, sep="\t", fill=TRUE, encoding="UTF-8")

lic_sales_lifetime<-read.delim("C:/Users/sbscu/Desktop/WMI-19-01/National Survey Effort/State License Data Tranfer Files/VA-DGIF/License_Sales_Lifetime.txt", header = TRUE, sep="\t", fill=TRUE, encoding="UTF-8")
```

Creating hunter dataset, and adding binary variables to indicate Annual and Combo license purchases 
```{r}
lic_sales_annual$LicenseID<-as.factor(as.character(
  lic_sales_annual$LicenseID))

annual_sales_type<-left_join(lic_sales_annual,lic,
                              by="LicenseID")

annual_sales_type$Combo<- 
  ifelse(annual_sales_type$Category == "Both H/F", 1, 0)

annual_sales_type$Annual<- 
  ifelse(annual_sales_type$Category == "Hunt", 1, 0)

cust$CustomerID<-as.numeric(as.character(cust$CustomerID))

hunters<-left_join(cust, annual_sales_type, by="CustomerID")
```

Adding Lifetime licenses to hunter dataset
```{r}
lifetime_sales_type<-left_join(lic_sales_lifetime,lic,
                              by="LicenseID")

lifetime_sales_type$Lifetime<- 
  ifelse(lifetime_sales_type$Category == "Hunt", 1, 0)

hunters<-left_join(hunters, lifetime_sales_type, by="CustomerID")
```

Adding license purchase observations to customer database (cust)
```{r}
#Combo Licenses______________________________________________
cust %>% group_by(CustomerID) 
filter(hunters, Combo>=1) 
y_customers <- as.data.frame(filter(hunters, Combo==1)) %>% 
  unique() %>% 
  select(CustomerID, Combo)
cust <- left_join(cust, y_customers, by = "CustomerID") %>% unique()
rm(y_customers)

#Annual Hunt Licenses________________________________________
filter(hunters, Annual>=1) 
y_customers <- as.data.frame(filter(hunters, Annual>=1)) %>% 
  unique() %>% 
  select(CustomerID, Annual)
cust <- left_join(cust, y_customers, by = "CustomerID") %>% unique()
rm(y_customers)

#Lifetime Hunt Licenses______________________________________
filter(hunters, Lifetime>=1) 
y_customers <- as.data.frame(filter(hunters, Lifetime>=1)) %>% 
  unique() %>% 
  select(CustomerID, Lifetime)
cust <- left_join(cust, y_customers, by = "CustomerID") %>% unique()
rm(y_customers)

#Turn NAs for missing licenses into 0s for counting purposes
cust[is.na(cust)] <- 0

#Dropping one observation with no data
cust<-cust[!(cust$CustomerID==0),]
```

Calculate age group based on birthdate
```{r}
cust$Birth_Date<-as.Date.factor(cust$Birth_Date)

cust$age <- 2019 - year(cust$Birth_Date)

cust$age_group <- 
  ifelse((0 <= cust$age & cust$age < 18), "17 or younger",
  ifelse((18 <= cust$age & cust$age <= 24), "18 to 24", 
  ifelse((25 <= cust$age & cust$age <= 34), "25 to 34", 
  ifelse((35 <= cust$age & cust$age <= 44), "35 to 44", 
  ifelse((45 <= cust$age & cust$age <= 54), "45 to 54", 
  ifelse((55 <= cust$age & cust$age <= 64), "55 to 64", 
  ifelse((65 <= cust$age), "65+", 
  "broken"
)))))))

#Dropping customers under 18
cust<-cust[!(cust$age_group=="17 or younger"),]
```

Printing Demographics for License Population
```{r}
#Age Groups
age_table<-cbind(table(cust$age_group),prop.table(table(cust$age_group)))
colnames(age_table)<-c("count","percent")

write.csv(age_table, file = "VA_hunter_age.csv")

#Gender
gender_table<-cbind(table(cust$Gender),prop.table(table(cust$Gender)))
colnames(gender_table)<-c("count","percent")

write.csv(gender_table, file = "VA_hunter_gender.csv")

#Annual License
annual_table<-cbind(table(cust$Annual),prop.table(table(cust$Annual)))
colnames(annual_table)<-c("count","percent")

write.csv(annual_table, file = "VA_Annual_Hunt_Lic.csv")

#Combo License
combo_table<-cbind(table(cust$Combo),prop.table(table(cust$Combo)))
colnames(combo_table)<-c("count","percent")

write.csv(combo_table, file = "VA_Combo_Hunt_Lic.csv")

#Lifetime License
lifetime_table<-cbind(table(cust$Lifetime),prop.table(table(cust$Lifetime)))
colnames(lifetime_table)<-c("count","percent")

write.csv(lifetime_table, file = "VA_Lifetime_Hunt_Lic.csv")
```

Creating subset of hunters with email addresses
```{r}
svy<-subset(cust,cust$eMail!="")

#Convert variable types to Factor
svy$age_group<-as.factor(svy$age_group)
svy$Combo<-as.factor(svy$Combo)
svy$Annual<-as.factor(svy$Annual)
svy$Lifetime<-as.factor(svy$Lifetime)
```

Defining Population Statistics
```{r}
pop <- list(
    age_group = c("18 to 24" = 0.104996733,
                  "25 to 34" = 0.153323259,
                  "35 to 44" = 0.148336002,
                  "45 to 54" = 0.185376363,
                  "55 to 64" = 0.192642798,
                  "65+" = 0.215324845),
    Gender = c("M" = 0.928353058, "F" = 0.058261143, 
               "U" = 0.013385799, "VA" = 0),
    Annual = c("0" = 0.427547616,"1" = 0.572452384),
    Combo = c("0" = 0.815426585,"1" = 0.184573415),
    Lifetime= c("0" = 0.745809457,"1" = 0.254190543))
```


Weighting function to be used on email list
```{r}
est_wts <- function(
    svy, pop, print_name = "", idvar = "CustomerID", cap = 20
) {
    # run weighting
    wts <- anesrake(pop, svy, caseid = svy[[idvar]], force1 = TRUE, cap = cap)
    
    # print summary
    cat("\nWeight Summary for", print_name, "-----------------------------\n\n")
    print(summary(wts))
    
    # return output
    svy$rake_wt <- wts$weightvec
    svy
}
```

Run Weighting
```{r}
cust_wt <- est_wts(svy, pop)
```

Pull weighted sample of 1000 emails
```{r}
va_email_list<-sample_n(cust_wt, 1000, weight = cust_wt$rake_wt)
write.csv(va_email_list, file = "VA_sample_contacts.csv")
```

Printing Demographics for sample
```{r}
#Age Groups
age_table<-cbind(table(va_email_list$age_group),prop.table(table(va_email_list$age_group)))
colnames(age_table)<-c("count","percent")

write.csv(age_table, file = "VA_sample_age.csv")

#Gender
gender_table<-cbind(table(va_email_list$Gender),prop.table(table(va_email_list$Gender)))
colnames(gender_table)<-c("count","percent")

write.csv(gender_table, file = "VA_sample_gender.csv")

#Annual License
annual_table<-cbind(table(va_email_list$Annual),prop.table(table(va_email_list$Annual)))
colnames(annual_table)<-c("count","percent")

write.csv(annual_table, file = "VA_sample_Annual_Hunt_Lic.csv")

#Combo License
combo_table<-cbind(table(va_email_list$Combo),prop.table(table(va_email_list$Combo)))
colnames(combo_table)<-c("count","percent")

write.csv(combo_table, file = "VA_sample_Combo_Hunt_Lic.csv")

#Lifetime License
lifetime_table<-cbind(table(va_email_list$Lifetime),prop.table(table(va_email_list$Lifetime)))
colnames(lifetime_table)<-c("count","percent")

write.csv(lifetime_table, file = "VA_sample_Lifetime_Hunt_Lic.csv")
```